---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Package description

<!-- badges: start -->

<!-- badges: end -->

The goal of intSurv is to estimate the heterogeneous treatment effect on the survival outcomes, combining the data from the randomized trial and observational studies. Under the proportional hazards assumption, the heterogeneous treatment effect function $\tau(X)$ is defined as the conditional hazard ratio of the potential survival times.

## Installation

You can install the development version of intSurv from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("siyi48/intSurv")
```

## Models

Let $X\in \mathbb{R}^d$ be the covariates, $A$ be the binary treatment, $S$ be the data source indicator, and $T$ be the survival time. Also, denote $\lambda_s(t\mid X, A=a)$ as the hazard function for the actual survival time in the data source $s$, where $s=1$ indicates the trial and $s=0$ indicates the observational studies. We posit the Cox models on each data source as 
$$
\begin{aligned}
\text{RCT:} \quad \lambda_1(t\mid X, A=a) & =\lambda_{1,0}(t)\exp\{c_1(X) + a\tau(X)\}; \\
\text{OS:} \quad \lambda_0(t\mid X, A=a) & =\lambda_{0,0}(t)\exp\{c_0(X) + a\tau(X) + a\lambda(X)\}.
\end{aligned}
$$
Here, $\tau(X)$ is the treatment effect function of interest, which is further assumed to be a linear structure as
$$
\tau(X) = \tau(X;\beta_0) = X^{\text T}\beta_0.
$$
We conduct sieve approximation on the nuisance functions $c_1(X), c_0(X)$, and $\lambda(X)$ using the polynomial basis. The integrative estimator is solved by minimizing the penalized log partial likelihood, with the penalty function selected as the adaptive lasso. We only add the penalization for the covariate information of $\lambda(X)$ (the confounding function), since other nuisance functions do not affect the efficiency of the integrative estimator. 

## Example

The main function `surv.hte` provides two types of estimated parameter $\beta$ in the treatment effect function $\tau(X)$ as `int` (the integrative estimator) and `rct` (the trial estimator).

```{r example}
library(intSurv)
## basic example code
q.c1 <- 3
q.c0 <- 3
q.lambda <- 3
nfolds <- 5 # initialize (use lasso value)
c1.mat <- matrix(dat$x1, ncol = 1)
c1.discrete <- matrix(dat$x2, ncol = 1)
c0.mat <- matrix(dat$x1, ncol = 1)
c0.discrete <- matrix(dat$x2, ncol = 1)
lambda.mat <-  matrix(dat$x1, ncol = 1)
lambda.discrete <- cbind(1, dat$x2)
tau.mat <- cbind(1, dat$x1, dat$x1^2)
s <- dat$s
delta <- dat$delta
t <- dat$t
a <- dat$a

res.hte <- surv.hte(tau.mat = tau.mat, c1.mat = c1.mat,
                    c1.discrete = c1.discrete, q.c1 = q.c1,
                    c0.mat = c0.mat, c0.discrete = c0.discrete, q.c0 = q.c0,
                    lambda.mat = lambda.mat,
                    lambda.discrete = lambda.discrete, q.lambda = q.lambda,
                    a = a, s = s, t = t, delta = delta,
                    nfolds = nfolds, type = c("int", "rct"))
res.hte
```


